---
title: "analysis"
---

## Goals for this notebook

Here's what we want to get done in this notebook:

- Separate each weather stations and unit into their own data frame
- Determine temperature differences
- Recombine all stations/units into one data frame

## Import data

```{r}
units <- read_rds("data-processed/01-heat-all.rds")

stations <- read_rds("data-processed/01-stations.rds")
```

## Separate Stations

Let's make each of our stations their own data frame.

```{r}
KRFI <- stations |> 
  filter(station_code == "KRFI")

KGOP <- stations |> 
  filter(station_code == "KGOP")

KGLS <- stations |> 
  filter(station_code == "KGLS")

KIAH <- stations |> 
  filter(station_code == "KIAH")

KEFD <- stations |> 
  filter(station_code == "KEFD")

KHOU <- stations |> 
  filter(station_code == "KHOU")

KLFK <- stations |> 
  filter(station_code == "KLFK")

KUTS <- stations |> 
  filter(station_code == "KUTS")

KMFE <- stations |> 
  filter(station_code == "KMFE")

KCOT <- stations |> 
  filter(station_code == "KCOT")

KHDO <- stations |> 
  filter(station_code == "KHDO")

KFST <- stations |> 
  filter(station_code == "KFST")

KELP <- stations |> 
  filter(station_code == "KELP")
```

## Separate Units

```{r}
units
```


Now let's separate units.

```{r}
hightower <- units |> 
  filter(unit == "Hightower")

plane <- units |> 
  filter(unit == "Plane")

# diboll <- units |> 
#   filter(unit == "Diboll")
# No unit data

# duncan <- units |> 
#   filter(unit == "Duncan")
# No unit data 

young <- units |> 
  filter(unit == "Young")

briscoe <- units |> 
  filter(unit == "Briscoe")

lopez <- units |> 
  filter(unit == "Lopez")

segovia <- units |> 
  filter(unit == "Segovia")

sanchez <- units |> 
  filter(unit == "Sanchez")

lynaugh <- units |> 
  filter(unit == "Lynaugh")

# fort_stockton <- units |> 
#   filter(unit == "Fort Stockton")
# No unit data

# galveston <- units |> 
#   filter(unit == "Galveston")
# No unit data

crain <- units |> 
  filter(unit == "Crain")

hilltop <- units |> 
  filter(unit == "Hilltop")

hughes <- units |> 
  filter(unit == "Hughes")

murray <- units |> 
  filter(unit == "Murray")

o_daniel <- units |> 
  filter(unit == "Mountain View")

woodman <- units |> 
  filter(unit == "Woodman")

bradshaw <- units |> 
  filter(unit == "Bradshaw")

# east_texas <- units |> 
#   filter(unit == "East Texas")
# No unit data

# ney <- units |> 
#   filter(unit == "Ney")
# No unit data

torres <- units |> 
  filter(unit == "Torres")

lychner <- units |> 
  filter(unit == "Lychner")

# kegans <- units |> 
#   filter(unit == "Kegans")
# No unit data

byrd <- units |> 
  filter(unit == "Byrd")
```

## Join dataframes

Let's put together the right station data with the right unit data.

```{r}
byrd_combined <- byrd |> 
  left_join(KUTS) |> 
  arrange(date)

byrd_combined
```

```{r}
lychner_combined <- lychner |> 
  left_join(KIAH) |> 
  arrange(date)

lychner_combined
```

```{r}
torres_combined <- torres |> 
  left_join(KIAH) |> 
  arrange(date)

torres_combined
```

```{r}
bradshaw_combined <- bradshaw |> 
  left_join(KRFI) |> 
  arrange(date)

bradshaw_combined
```

```{r}
woodman_combined <- woodman |> 
  left_join(KGOP) |> 
  arrange(date)

woodman_combined
```

```{r}
o_daniel_combined <- o_daniel |> 
  left_join(KGOP) |> 
  arrange(date)

o_daniel_combined
```

```{r}
murray_combined <- murray |> 
  left_join(KGOP) |> 
  arrange(date)

murray_combined
```

```{r}
hughes_combined <- hughes |> 
  left_join(KGOP) |> 
  arrange(date)

hughes_combined
```

```{r}
hilltop_combined <- hilltop |> 
  left_join(KGOP) |> 
  arrange(date)

hilltop_combined
```

```{r}
crain_combined <- crain |> 
  left_join(KGOP) |> 
  arrange(date)

crain_combined
```

```{r}
lynaugh_combined <- lynaugh |> 
  left_join(KFST) |> 
  arrange(date)

lynaugh_combined
```

```{r}
sanchez_combined <- sanchez |> 
  left_join(KELP) |> 
  arrange(date)

sanchez_combined
```

```{r}
segovia_combined <- segovia |> 
  left_join(KMFE) |> 
  arrange(date)

segovia_combined
```

```{r}
lopez_combined <- lopez |> 
  left_join(KMFE) |> 
  arrange(date)

lopez_combined
```

```{r}
briscoe_combined <- briscoe |> 
  left_join(KCOT) |> 
  arrange(date)

briscoe_combined
```

```{r}
young_combined <- young |> 
  left_join(KEFD) |> 
  arrange(date)

young_combined
```

```{r}
# plane |> 
#   left_join(KT41) |> 
#   arrange(date)
# Station data unavailable
```

```{r}
# hightower |> 
#   left_join(KT41) |> 
#   arrange(date)
# Station data unavailable
```

## Combine all comparable data

Now let's add all of our comparable data together. First, we have to make a list of all our units.

```{r}
all <- list(bradshaw_combined, briscoe_combined, byrd_combined, crain_combined, hilltop_combined, hughes_combined, lopez_combined, lychner_combined, lynaugh_combined, murray_combined, o_daniel_combined, sanchez_combined, segovia_combined, torres_combined, woodman_combined, young_combined)
```

Now we can join them together.

```{r}
jails_combined <- all |> 
  list_rbind()

jails_combined
```

## Make the temperature difference column

Time to get to the whole point of this project! Let's create a column that is the difference between the unit temperature and the station temperature.

```{r}
jails_diff <- jails_combined |> 
  mutate(temp_diff = unit_temp - station_temp)

jails_diff
```

## Rearrange columns

Nice! Now we just need to switch the order of our date and unit columns. 

```{r}
ali_final_comparison <- jails_diff |> 
  relocate(unit, .after = date)

ali_final_comparison
```

## Export data

Time for the final step: let's export.

```{r}
ali_final_comparison |> 
  write_rds("data-processed/ali-final-comparison.rds")
```

