---
title: "Station Cleaning"
---

In order to compare our prison unit temperatures to the actual temperatures, we need to pull data from the National Weather Service website. Let's work on importing and cleaning that data.

## Goals for this notebook

Steps we'll take to prepare our data:

- Download the data
- Import it into our notebook
- Clean up the data types and columns
- Export the data for the next notebook

## Set up

Let's load our libraries to start.

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(janitor)
```

## Import data

Now let's download our data. To start that process, we'll create a vector for all of our weather station files.

```{r}
files <-
list.files(
  "data-raw/weather_stations",
  pattern = ".csv",
  full.names = TRUE
) 

files
```

## Read in our files

Let's read the csv's and bind them together into one data frame.

```{r}
stations <- files |> 
  set_names(basename) |> 
map(
    read_csv,
    col_select = c(STATION, DATE, HourlyDryBulbTemperature)
  ) |> 
  list_rbind() |> 
  clean_names() |> 
  mutate(
    station = as.character(station)
  )

stations
```

## Add station names

Let's code a function so we can know the station names

```{r}
named_stations <- stations |> 
  mutate( 
    station_code = case_match(station, 
                             "72057700175" ~ "KRFI",
                             "72232300362" ~ "KGOP",
                             "72242012923" ~ "KGLS",
                             "72243012960" ~ "KIAH",
                             "72243612906" ~ "KEFD",
                             "72244012918" ~ "KHOU",
                             "72244693987" ~ "KLFK",
                             "72244753903" ~ "KUTS",
                             "72250612959" ~ "KMFE",
                             "72252612947" ~ "KCOT",
                             "72253312962" ~ "KHDO",
                             "72261823091" ~ "KFST",
                             "72270023044" ~ "KELP"
                            )
  ) |>
  select(!station) |> 
  mutate(station_date = date(date))

named_stations
```

## Remove unnecessary values

We only need temperature reads near 15:00 and dates from April to September, so let's get rid of all other values.

```{r}
filtered_stations <- named_stations |> 
    filter(
      date >= "2023-04-01",
      date < "2023-10-01"
    ) |> 
  filter(hour(date) == 14) |> 
  group_by(station_code, station_date) |> 
  slice_max(minute(date)) |> 
  select(!date)
  
filtered_stations
```

```{r}
stations_clean <- filtered_stations |> 
  mutate(station_temp = hourly_dry_bulb_temperature) |> 
  mutate(date = station_date) |> 
  group_by(date, station_code) |> 
  select(!c(hourly_dry_bulb_temperature, station_date))

stations_clean
```

## Export the data

Now let's export.

```{r}
stations_clean |> 
  write_rds("data-processed/01-stations.rds")
```

