---
title: "johan-final-comparison-all"
---

## Loading in libaries

Setting up my libraries.

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(janitor)
library(dplyr)
library(lubridate)
```

## Importing `final comparison's`

I’m importing the final comparison RDS files, so that I can later combine them using rbind.

```{r}
#| label: importing comparisons
ali <- read_rds("data-processed/ali-final-comparison.rds")
johan <- read_rds("data-processed/johan-final-comparison.rds")
karina <- read_rds("data-processed/karina-final-comparison.rds")
pearson <- read_rds("data-processed/pearson-final-comparison.rds")
```

## Binding `final comparison's`

We are flagging any temperature difference greater than or equal to 15 degrees Fahrenheit and 0 degrees Fahrenheit as notable. We renamed the Mountain View unit to change to the new name to join correctly.

```{r}
#| label: cleaning flagged data
final <- rbind(ali, johan, karina, pearson)

unit_flagged <- final |> 
  arrange(temp_diff |> desc()) |> 
  filter(temp_diff >= 15 | temp_diff == 0)

unit_flagged[40, 2] = "O'Daniel"

unit_flagged
```


## Importing `unit_info`

I’m importing the created spreadsheet with collected unit information and cleaning the names.

```{r}
#| label: importing unit_info
units <- read_csv("data-raw/unit_info_altered.csv")

unit_info <- units |> clean_names()

unit_info
```

## Cleaning `unit_info`

I’m changing the column names to better fit our final comparison list, and selecting only the columns we need.

```{r}
#| label: cleaning
 unit_info_c <- unit_info |> 
  rename(unit = unit_name) |>
  select(unit, type, region, established)

unit_info_c
```

## Joining

Now, let’s join our final comparison data with our new information by unit.

```{r}
#| label: full join
unit_info_join <- unit_flagged |> 
  left_join(unit_info_c, by = "unit") |> 
  select(date, type, region, established, unit, unit_temp, station_code, station_temp, temp_diff)

unit_info_join
```

## Grouping by `prison type`

Now, we want to group by prison type to see which types of prisons have more flagged days.

```{r}
#| label: type
type_count <- unit_info_join |> 
  select(date, type, unit, station_code, station_temp, temp_diff) |> 
  group_by(type) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))

type_count
```

## Grouping by `region`

Now, we want to group by region to see which regions of prisons have more flagged days.

```{r}
#| label: region
region_count <- unit_info_join |> 
  select(date, region, unit, station_code, station_temp, temp_diff) |> 
  group_by(region) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))

region_count
```

## Grouping by `age of prison`

Now, we want to group by the age of the prison to determine if the building’s age is associated with having more flagged days.

```{r}
#| label: age
age_count <- unit_info_join |> 
  select(date, established, unit, station_code, station_temp, temp_diff) |> 
  group_by(established) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))

age_count
```

## Grouping by `unit`

Now, we want to group by unit to see which units have more flagged days.

```{r}
unit_count <- unit_info_join |> 
  select(date, region, unit, station_code, station_temp, temp_diff) |> 
  group_by(unit) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))

unit_count
```

## Charts

Finally, we are creating individual charts to visualize the difference between unit and station temperatures.

```{r}
#| label: facets

units <- unique(final$unit)
for (unit_name in units) {
  df <- subset(final, unit == unit_name)
  
p <- ggplot(df, aes(x = date)) +
  geom_line(aes(y = unit_temp, color = "Unit Temp")) +
  geom_line(aes(y = station_temp, color = "Station Temp")) +
  labs(
    title = paste("Temperature Trends for Unit:", unit_name),
    x = "Date",
    y = "Temperature"
  ) +
  ylim(0, 120) +
  theme_minimal()

print(p)
}
```

## Analysis of `prison type` grouping

```{r}
#| label: specific prison
unit_info_join |> 
  select(date, type, unit, station_code, station_temp, temp_diff) |> 
  filter(type == "Prison") |>
  group_by(unit) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))
```

```{r}
#| label: specific state jail
unit_info_join |> 
  select(date, type, unit, station_code, station_temp, temp_diff) |> 
  filter(type == "State Jail") |>
  group_by(unit) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))
```

## Analysis of `Region` grouping

```{r}
#| label: region V 
unit_info_join |> 
  select(date, region, unit, station_code, station_temp, temp_diff) |> 
  filter(region == "V") |> 
  group_by(unit) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))
```

```{r}
#| label: region IV 
unit_info_join |> 
  select(date, region, unit, station_code, station_temp, temp_diff) |> 
  filter(region == "IV") |> 
  group_by(unit) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))
```

## Analysis of `prison age` grouping

```{r}
#| label: age
unit_info_join |> 
  select(date, established, unit, station_code, station_temp, temp_diff) |> 
  filter(established == "1995") |> 
  group_by(unit) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))
```

```{r}
#| label: age
unit_info_join |> 
  select(date, established, unit, station_code, station_temp, temp_diff) |> 
  filter(established == "1994") |> 
  group_by(unit) |> 
  summarise(number_of_days_over_15 = n()) |> 
  arrange(desc(number_of_days_over_15))
```