---
title: "johan-02-cleaning"
format: html
---

## Goals of this notebook

What we'll do to prepare the data:

- Download the data
- Import it into our notebook
- Clean up data types and columns 
- Export data into our next notebook

## Loading in library

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(janitor)
library(dplyr)
library(lubridate)
```

## Importing NWS Data

We only need name, date and temperature from the NWS csv's

```{r}
#| label: columns
col_list <- c(
  "NAME",
  "DATE",
  "HourlyDryBulbTemperature"
  )
```

This will create a file list to be able to import all of our data from my `station_data` folder

```{r}
#| label: files

## Create a list of files in the station_data folder
station_files_list <- list.files(
  "data-raw/johan_stations",
  pattern = "\\.csv",
  full.name = TRUE
)
```

Using Pearson's function to create the data table. This will change the names of the columns to something more appropriate. I want to do this to be able to delete the `datetime` column. Since the indoor data we have is only for april and sept, we will filter to those months. Also, we need to note that some prisons might not have data and we might have data for prison that we dont have indoor data for.

```{r}
#| label: function

## Define the function to process each file and rename the column
process_file <- function(path, station_name) {
  # Read the CSV file and select specific columns
  df <- read_csv(path, col_select = col_list)
  
  # Process the data and rename the HourlyDryBulbTemperature column
  df |> 
    filter(hour(DATE) == 14) |> 
    group_by(date(DATE)) |> 
    slice_max(minute(DATE)) |> 
    rename(!!station_name := HourlyDryBulbTemperature) |> # Rename the temperature column to station name
    clean_names() |> 
    rename(date = date_date, datetime = date, station_location = name) |> 
    filter(month(date) %in% 4:9) |> 
    mutate(hour_temp_taken = format(datetime, "%H:%M:%S")) |> 
    select(-datetime)
}

## Create an empty list to store the dataframes
station_dataframes <- list()

## Process each file and rename the column dynamically
for (file_path in station_files_list) {
  # Extract the station name from the file name
  station_name <- tools:: file_path_sans_ext(basename(file_path))
  
  # Process the file and add it to the list
  station_dataframes[[station_name]] <- process_file(file_path, station_name = station_name)
}

## Assign each dataframe to the global environment
list2env(station_dataframes, envir = .GlobalEnv)

## Print the names of the created dataframes
print(names(station_dataframes))
```

## Export

We are done with this lets do some analysis!

```{r}
#| label: export

output_folder <- "data-processed/station-processed" # Specify the output folder

for (station_name in names(station_dataframes)) {
  output_path <- file.path(output_folder, paste0(station_name, ".csv")) # File path
  write_csv(station_dataframes[[station_name]], output_path)           # Write the dataframe
}

cat("All dataframes have been exported to the 'data-processed/' folder.\n")
```























