---
title: "Analysis"
---

## Goals of this notebook

Combine cleaned indoor data with the closest national weather station data.

- Import all weather station data
- Combine each weather station to its corresponding prison
- Create `difference` column

## Loading Library

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(janitor)
library(dplyr)
library(lubridate)
```

## Importing both data sets

First, I'm importing indoor files.

```{r}
#| label: indoor

indoor_heat_all <- read_rds("data-processed/johan-01-heat-all.rds")

indoor_heat_all
```

Secondly, I'm importing all the national weather station data that was cleaned.

```{r}
#| label: indoor
#| message: false

station_files_list <- list.files(
  "data-processed/station-processed",
  pattern = "\\.csv",
  full.name = TRUE
)

# Read the CSV files into a named list of data frames
station_data <- lapply(station_files_list, read_csv)

# Name the elements of the list based on the file names (without extensions)
names(station_data) <- tools::file_path_sans_ext(basename(station_files_list))

# Use list2env to create variables in the global environment
list2env(station_data, envir = .GlobalEnv)

cat("The following objects have been created in the global environment:\n")
print(ls())
```

## Jordan & KPPA Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: jordan indoor

jordan <- indoor_heat_all |> 
  filter(unit == "Jordan") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

jordan
```

```{r}
#| label: join kppa

KPPA_JORDAN <- jordan |> 
  left_join(KPPA, by = "date") |> 
  select(date, unit_name, indoor_temp, kppa) |> 
  mutate(difference = abs(indoor_temp - kppa))

name = toupper(colnames(KPPA_JORDAN)[4])
KPPA_JORDAN <- KPPA_JORDAN |> mutate(station_code = name) |> 
  rename(station_temp = kppa) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KPPA_JORDAN

```

## Formby & KPVW Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: formby indoor

formby <- indoor_heat_all |> 
  filter(unit == "Formby") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

formby
```


```{r}
#| label: join kpvw

KPVW_FORMBY <- formby  |> 
  left_join(KPVW, by = "date") |> 
  select(date, unit_name, indoor_temp, kpvw) |> 
  mutate(difference = abs(indoor_temp - kpvw))

name = toupper(colnames(KPVW_FORMBY)[4])
KPVW_FORMBY <- KPVW_FORMBY |> mutate(station_code = name) |> 
  rename(station_temp = kpvw) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KPVW_FORMBY
```

## Wheeler & KPVW Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: wheeler indoor

wheeler <- indoor_heat_all |> 
  filter(unit == "Wheeler") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

wheeler
```

```{r}
#| label: join kpvw

KPVW_WHEELER <- wheeler |> 
  left_join(KPVW, by = "date") |> 
  select(date, unit_name, indoor_temp, kpvw) |> 
  mutate(difference = abs(indoor_temp - kpvw))

name = toupper(colnames(KPVW_WHEELER)[4])
KPVW_WHEELER <- KPVW_WHEELER |> mutate(station_code = name) |> 
  rename(station_temp = kpvw) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KPVW_WHEELER
```

## Memorial & KLVJ Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: memorial indoor

memorial <- indoor_heat_all |> 
  filter(unit == "Memorial") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

memorial
```

```{r}
#| label: join klvj

KLVJ_MEMORIAL <- memorial |> 
  left_join(KLVJ, by = "date") |> 
  select(date, unit_name, indoor_temp, klvj) |> 
  mutate(difference = abs(indoor_temp - klvj))

name = toupper(colnames(KLVJ_MEMORIAL)[4])
KLVJ_MEMORIAL <- KLVJ_MEMORIAL |> mutate(station_code = name) |> 
  rename(station_temp = klvj) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KLVJ_MEMORIAL
```

## Ramsey & KLVJ Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: ramsey indoor

ramsey <- indoor_heat_all |> 
  filter(unit == "Ramsey") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

ramsey
```

```{r}
#| label: join klvj

KLVJ_RAMSEY <- ramsey |> 
  left_join(KLVJ, by = "date") |> 
  select(date, unit_name, indoor_temp, klvj) |> 
  mutate(difference = abs(indoor_temp - klvj))

name = toupper(colnames(KLVJ_RAMSEY)[4])
KLVJ_RAMSEY <- KLVJ_RAMSEY |> mutate(station_code = name) |> 
  rename(station_temp = klvj) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KLVJ_RAMSEY
```

## Stringfellow & KLVJ Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: stringfellow indoor

stringfellow <- indoor_heat_all |> 
  filter(unit == "Stringfellow") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

stringfellow
```

```{r}
#| label: join klvj

KLVJ_STRINGFELLOW <- stringfellow |> 
  left_join(KLVJ, by = "date") |> 
  select(date, unit_name, indoor_temp, klvj) |> 
  mutate(difference = abs(indoor_temp - klvj))

name = toupper(colnames(KLVJ_STRINGFELLOW)[4])
KLVJ_STRINGFELLOW <- KLVJ_STRINGFELLOW |> mutate(station_code = name) |> 
  rename(station_temp = klvj) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |>  
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KLVJ_STRINGFELLOW
```

## Terrell & KLVJ Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: terrell indoor

terrell <- indoor_heat_all |> 
  filter(unit == "Terrell") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

terrell
```

```{r}
#| label: join klvj

KLVJ_TERRELL <- terrell |> 
  left_join(KLVJ, by = "date") |> 
  select(date, unit_name, indoor_temp, klvj) |> 
  mutate(difference = abs(indoor_temp - klvj))

name = toupper(colnames(KLVJ_TERRELL)[4])
KLVJ_TERRELL <- KLVJ_TERRELL |> mutate(station_code = name) |> 
  rename(station_temp = klvj) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KLVJ_TERRELL
```

## Dominguez & KSKF Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: dominguez indoor

dominguez <- indoor_heat_all |> 
  filter(unit == "Dominguez") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

dominguez
```

```{r}
#| label: join kskf

KSKF_DOMINGUEZ <- dominguez |> 
  left_join(KSKF, by = "date") |> 
  select(date, unit_name, indoor_temp, kskf) |> 
  mutate(difference = abs(indoor_temp - kskf))

name = toupper(colnames(KSKF_DOMINGUEZ)[4])
KSKF_DOMINGUEZ <- KSKF_DOMINGUEZ |> mutate(station_code = name) |> 
  rename(station_temp = kskf) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    date >= as.Date("2023-06-20") & date <= as.Date("2023-06-22") ~ "active",
    date >= as.Date("2023-07-13") & date <= as.Date("2023-07-15") ~ "active",
    (date >= as.Date("2023-07-11") & date <= as.Date("2023-07-12")) |
      (date >= as.Date("2023-07-16") & date <= as.Date("2023-07-17")) ~ "adjacent",
    (date >= as.Date("2023-06-18") & date <= as.Date("2023-06-19")) |
      (date >= as.Date("2023-06-23") & date <= as.Date("2023-06-24")) ~ "adjacent",
    TRUE ~ "inactive"
  ))

KSKF_DOMINGUEZ
```

## Daniel & KSNK Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: daniel indoor

daniel <- indoor_heat_all |> 
  filter(unit == "Daniel") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

daniel
```

```{r}
#| label: join ksnk

KSNK_DANIEL <- daniel |> 
  left_join(KSNK, by = "date") |> 
  select(date, unit_name, indoor_temp, ksnk) |> 
  mutate(difference = abs(indoor_temp - ksnk))

name = toupper(colnames(KSNK_DANIEL)[4])
KSNK_DANIEL <- KSNK_DANIEL |> mutate(station_code = name) |> 
  rename(station_temp = ksnk) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KSNK_DANIEL
```

## Boyd & KLXY Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: boyd indoor

boyd <- indoor_heat_all |> 
  filter(unit == "Boyd") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

boyd
```

```{r}
#| label: join klxy

KLXY_BOYD <- boyd |> 
  left_join(KLXY, by = "date") |> 
  select(date, unit_name, indoor_temp, klxy) |> 
  mutate(difference = abs(indoor_temp - klxy))

name = toupper(colnames(KLXY_BOYD)[4])
KLXY_BOYD <- KLXY_BOYD |> mutate(station_code = name) |> 
  rename(station_temp = klxy) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KLXY_BOYD
```

## Beto & KPSN Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: beto indoor

beto <- indoor_heat_all |> 
  filter(unit == "Beto") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

beto
```

```{r}
#| label: join kpsn

KPSN_BETO <- beto |> 
  left_join(KPSN, by = "date") |> 
  select(date, unit_name, indoor_temp, kpsn) |> 
  mutate(difference = abs(indoor_temp - kpsn))

name = toupper(colnames(KPSN_BETO)[4])
KPSN_BETO <- KPSN_BETO |> mutate(station_code = name) |> 
  rename(station_temp = kpsn) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KPSN_BETO
```

## Coffield & KPSN Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: coffield indoor

coffield <- indoor_heat_all |> 
  filter(unit == "Coffield") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

coffield
```

```{r}
#| label: join kpsn

KPSN_COFFIELD <- coffield |> 
  left_join(KPSN, by = "date") |> 
  select(date, unit_name, indoor_temp, kpsn) |> 
  mutate(difference = abs(indoor_temp - kpsn))

name = toupper(colnames(KPSN_COFFIELD)[4])
KPSN_COFFIELD <- KPSN_COFFIELD |> mutate(station_code = name) |> 
  rename(station_temp = kpsn) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KPSN_COFFIELD
```

## Michael & KPSN Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: michael indoor

michael <- indoor_heat_all |> 
  filter(unit == "Michael") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

michael
```

```{r}
#| label: join kpsn

KPSN_MICHAEL <- coffield |> 
  left_join(KPSN, by = "date") |> 
  select(date, unit_name, indoor_temp, kpsn) |> 
  mutate(difference = abs(indoor_temp - kpsn))

name = toupper(colnames(KPSN_MICHAEL)[4])
KPSN_MICHAEL <- KPSN_MICHAEL |> mutate(station_code = name) |> 
  rename(station_temp = kpsn) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    TRUE ~ "inactive"
  ))

KPSN_MICHAEL
```

## Johnston & KJDD Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: johnston indoor

johnston <- indoor_heat_all |> 
  filter(unit == "Johnston") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

johnston
```

```{r}
#| label: join kjdd

KJDD_JOHNSTON <- johnston |> 
  left_join(KJDD, by = "date") |> 
  select(date, unit_name, indoor_temp, kjdd) |> 
  mutate(difference = abs(indoor_temp - kjdd))

name = toupper(colnames(KJDD_JOHNSTON)[4])
KJDD_JOHNSTON <- KJDD_JOHNSTON |> mutate(station_code = name) |> 
  rename(station_temp = kjdd) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when( 
    TRUE ~ "inactive")) # creating inactive status

KJDD_JOHNSTON
```

## Lewis & KJAS Join

Now, I will join the prison with the corresponding weather station data and create a difference column.

```{r}
#| label: lewis

lewis <- indoor_heat_all |> 
  filter(unit == "Lewis") |> 
  arrange(date) |> 
  rename(indoor_temp = temperature, unit_name = unit)

lewis
```

```{r}
#| label: join kjas

KJAS_LEWIS <- lewis |> 
  left_join(KJAS, by = "date") |> 
  select(date, unit_name, indoor_temp, kjas) |> 
  mutate(difference = abs(indoor_temp - kjas))

name = toupper(colnames(KJAS_LEWIS)[4])
KJAS_LEWIS <- KJAS_LEWIS |> mutate(station_code = name) |> 
  rename(station_temp = kjas) |> 
  select(date, unit_name, indoor_temp, station_code, station_temp, difference) |> 
  mutate(status = case_when(
    date >= as.Date("2023-08-02") & date <= as.Date("2023-08-28") ~ "active", 
    (date >= as.Date("2023-07-31") & date <= as.Date("2023-08-01")) |
      (date >= as.Date("2023-08-29") & date <= as.Date("2023-08-30")) ~ "adjacent",
    TRUE ~ "inactive"  # All other cases
  ))

KJAS_LEWIS
```

## Export

Nice Job! We are done doing them individually. Now, we want to join them all to create one long pivot.

```{r}
#| label: export

KPPA_JORDAN |> write_csv("data-processed/stations_join/KPPA_JORDAN.csv")
KPVW_FORMBY |> write_csv("data-processed/stations_join/KPVW_FORMBY.csv")
KPVW_WHEELER |> write_csv("data-processed/stations_join/KPVW_WHEELER.csv")
KLVJ_MEMORIAL |> write_csv("data-processed/stations_join/KLVJ_MEMORIAL.csv")
KLVJ_RAMSEY |> write_csv("data-processed/stations_join/KLVJ_RAMSEY.csv")
KLVJ_STRINGFELLOW |> write_csv("data-processed/stations_join/KLVJ_STRINGFELLOW.csv")
KLVJ_TERRELL |> write_csv("data-processed/stations_join/KLVJ_TERRELL.csv")
KSKF_DOMINGUEZ |> write_csv("data-processed/stations_join/KSKF_DOMINGUEZ.csv")
KSNK_DANIEL |> write_csv("data-processed/stations_join/KSNK_DANIEL.csv")
KLXY_BOYD |> write_csv("data-processed/stations_join/KLXY_BOYD.csv")
KPSN_BETO |> write_csv("data-processed/stations_join/KPSN_BETO.csv")
KPSN_COFFIELD |> write_csv("data-processed/stations_join/KPSN_COFFIELD.csv")
KPSN_MICHAEL |> write_csv("data-processed/stations_join/KPSN_MICHAEL.csv")
KJDD_JOHNSTON |> write_csv("data-processed/stations_join/KJDD_JOHNSTON.csv")
KJAS_LEWIS |> write_csv("data-processed/stations_join/KJAS_LEWIS.csv")
```

## Full Join

Now, we want to join them all to create one long pivot.

```{r}
#| label: full join

combined_units <- bind_rows(KPPA_JORDAN, KPVW_FORMBY, KPVW_WHEELER, KLVJ_MEMORIAL, KLVJ_RAMSEY, KLVJ_STRINGFELLOW, KLVJ_TERRELL, KSKF_DOMINGUEZ, KSNK_DANIEL, KLXY_BOYD, KPSN_BETO, KPSN_COFFIELD, KPSN_MICHAEL, KJDD_JOHNSTON, KJAS_LEWIS)

combined_units
``` 

# Export Cleaning

```{r}
#| label: final cleaning

unit_final <- combined_units |> 
  rename(unit = unit_name, unit_temp = indoor_temp, temp_diff = difference)

unit_final
```

```{r}
#| label: final export

unit_final |> write_rds("data-processed/johan-final-comparison.rds")
```

