---
title: "Comparison"
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(janitor)
library(lubridate)
```

## Importing the cleaned data

This code chunk will import the data for comparison

```{r}
#| label: importing

indoor_temps <- read_rds("data-processed/01-heat-all.rds")
KABI_temps <- read_rds("data-processed/KABI.rds")
KAMA_temps <- read_rds("data-processed/KAMA.rds")
KBEA_temps <- read_rds("data-processed/KBEA.rds")
KBKD_temps <- read_rds("data-processed/KBKD.rds")
KBMQ_temps <- read_rds("data-processed/KBMQ.rds")
KBPT_temps <- read_rds("data-processed/KBPT.rds")
KBWD_temps <- read_rds("data-processed/KBWD.rds")
KCDS_temps <- read_rds("data-processed/KCDS.rds")
KCLL_temps <- read_rds("data-processed/KCLL.rds")
KEDC_temps <- read_rds("data-processed/KEDC.rds")
KXBP_temps <- read_rds("data-processed/KXBP.rds")
KLBX_temps <- read_rds("data-processed/KLBX.rds")
KVCT_temps <- read_rds("data-processed/KVCT.rds")
KSNK_temps <- read_rds("data-processed/KSNK.rds")
KRBD_temps <- read_rds("data-processed/KRBD.rds")
KDHT_temps <- read_rds("data-processed/KDHT.rds")

indoor_temps |> glimpse()
```

## Filtering for unit

This code chunk will create dataframes for each unit.

```{r}
#| label: units

Middleton <- indoor_temps |> 
  filter(unit == "Middleton")

Robertson <- indoor_temps |> 
  filter(unit == "Robertson")

Clements <- indoor_temps |> 
  filter(unit == "Clements")

Gist <- indoor_temps |> 
  filter(unit == "Gist")

Stiles <- indoor_temps |> 
  filter(unit == "Stiles")

Garza_West <- indoor_temps |> 
  filter(unit == "Garza West")

McConnell <- indoor_temps |> 
  filter(unit == "Mcconnell")

#cole and moore if station is found

Clemens <- indoor_temps |> 
  filter(unit == "Clemens")

Roach <- indoor_temps |> 
  filter(unit == "Roach")

Wallace <- indoor_temps |> 
  filter(unit == "Wallace")

Stevenson <- indoor_temps |> 
  filter(unit == "Stevenson")

Dalhart <- indoor_temps |> 
  filter(unit == "Dalhart")

Hutchins <- indoor_temps |> 
  filter(unit == "Hutchins")
```

## Joining the data

This set of code chunks will combine each unit with the corresponding station and find the difference in temperature between the two.

```{r}
#| label: Middleton

Middleton_comp <- left_join(Middleton, KABI_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Middleton_comp
```

```{r}
#| label: Robertson

Robertson_comp <- left_join(Robertson, KABI_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Robertson_comp
```

```{r}
#| label: Clements

Clements_comp <- left_join(Clements, KAMA_temps, by = "date") |> 
    mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Clements_comp
```

```{r}
#| label: Gist

Gist_comp <- left_join(Gist, KBPT_temps, by = "date") |> 
    mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Gist_comp
```

```{r}
#| label: Stiles

Stiles_comp <- left_join(Stiles, KBPT_temps, by = "date") |> 
    mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Stiles_comp
```

```{r}
#| label: Garza West

Garza_West_comp <- left_join(Garza_West, KBEA_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Garza_West_comp
```

```{r}
#| label: McConnell

McConnell_comp <- left_join(McConnell, KBEA_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

McConnell_comp
```

```{r}
#| label: Clemens

Clemens_comp <- left_join(Clemens, KLBX_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Clemens_comp
```


```{r}
#| label: Roach

Roach_comp <- left_join(Roach, KCDS_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Roach_comp
```

```{r}
#| label: Wallace

Wallace_comp <- left_join(Wallace, KSNK_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Wallace_comp
```

```{r}
#| label: Stevenson

Stevenson_comp <- left_join(Stevenson, KVCT_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Stevenson_comp
```

```{r}
#| label: Dalhart

Dalhart_comp <- left_join(Dalhart, KDHT_temps, by = "date") |>
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Dalhart_comp
```

```{r}
#| label: Hutchins

Hutchins_comp <- left_join(Hutchins, KRBD_temps, by = "date") |>
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, difference)

Hutchins_comp
```

```{r}
#|label: joining all frames

all_comps <- bind_rows(Middleton_comp, Robertson_comp, Clements_comp, Gist_comp, Stiles_comp, Garza_West_comp, McConnell_comp, Clemens_comp, Roach_comp, Wallace_comp, Stevenson_comp, Dalhart_comp, Hutchins_comp) |> 
  rename(unit_temp = temperature, station_code = station, station_temp = hourly_temp, temp_diff = difference)

all_comps
```

## Exporting comparison

This code chunk will export the data

```{r}
#| label: exporting

all_comps |> 
  write_rds("data-processed/pearson-final-comparison.rds")
```

