---
title: "Activation Analysis"
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(janitor)
library(lubridate)
library(plotly)
```

## Importing Unit-Weather Station Data

This code chunk will import the unit and weather station combined data for each person.

```{r}
#| label: importing comparisons

ali_units_weather <- read_rds("data-processed/ali-final-comparison.rds")
johan_units_weather <- read_rds("data-processed/johan-final-comparison.rds")
karina_units_weather <- read_rds("data-processed/karina-final-comparison.rds")
pearson_units_weather <- read_rds("data-processed/pearson-final-comparison.rds")
```


## Importing Activation Data

This code chunk will import the cleaned activation data

```{r}
cleaned_activation_data <- read_rds("data-processed/pearson-activation-data.rds")
```

## Combining Unit-Weather Data

This code chunk will combine the separate comparisons into one total comparison.

```{r}
#| label: total comparison

all_units_weather <- rbind(ali_units_weather, johan_units_weather, karina_units_weather, pearson_units_weather)

all_units_weather
```

## Combining Activation and Unit Data

This code chunk will combine the activation and unit data based on the unit impacted.

```{r}
#| label: combining unit and activation


activation_unit_combined <- all_units_weather |> 
  left_join(cleaned_activation_data, by = c("unit" = "unit", "date" = "ics_implementation_date"))
```

## Charts

This code chunk will create charts that visualize the difference between unit and station temperature using the code write by Johan, modified to highlight certain areas. The bold part of each line represents when the ICS is in effect.

```{r}
#| label: charts
  
units <- unique(activation_unit_combined$unit)
for (unit_name in units) {
  df <- subset(activation_unit_combined, unit == unit_name)
  
ac <- ggplot(df, aes(x = date)) +
  geom_line(aes(y = unit_temp, color = "Unit Temp")) +
  geom_line(aes(y = station_temp, color = "Station Temp")) +
  geom_point(aes(x = ics_initiated_date, y = unit_temp)) +
  geom_point(aes(x = ics_deactivated_date, y = unit_temp)) +
  scale_color_manual(values = c("red", "blue")) +
  labs(
    title = paste("Temperature Trends for Unit:", unit_name),
    x = "Date",
    y = "Temperature"
  ) +
  ylim(0, 120) +
  theme_minimal()

print(ac)
}
```

