---
title: "Comparison"
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(janitor)
library(lubridate)
```

## Importing the cleaned data

This code chunk will import the data for comparison

```{r}
#| label: importing

indoor_temps <- read_rds("data-processed/pearson-01-heat-all.rds")
KABI_temps <- read_rds("data-processed/KABI.rds")
KAMA_temps <- read_rds("data-processed/KAMA.rds")
KBEA_temps <- read_rds("data-processed/KBEA.rds")
KBKD_temps <- read_rds("data-processed/KBKD.rds")
KBMQ_temps <- read_rds("data-processed/KBMQ.rds")
KBPT_temps <- read_rds("data-processed/KBPT.rds")
KBWD_temps <- read_rds("data-processed/KBWD.rds")
KCDS_temps <- read_rds("data-processed/KCDS.rds")
KCLL_temps <- read_rds("data-processed/KCLL.rds")
KEDC_temps <- read_rds("data-processed/KEDC.rds")
KXBP_temps <- read_rds("data-processed/KXBP.rds")
KLBX_temps <- read_rds("data-processed/KLBX.rds")
KVCT_temps <- read_rds("data-processed/KVCT.rds")
KSNK_temps <- read_rds("data-processed/KSNK.rds")
KRBD_temps <- read_rds("data-processed/KRBD.rds")
KDHT_temps <- read_rds("data-processed/KDHT.rds")

activation_status <- read_rds("data-processed/pearson-activation-data.rds")

indoor_temps |> glimpse()
```

## Filtering for unit

This code chunk will create dataframes for each unit.

```{r}
#| label: units

Middleton <- indoor_temps |> 
  filter(unit == "Middleton")

Robertson <- indoor_temps |> 
  filter(unit == "Robertson")

Clements <- indoor_temps |> 
  filter(unit == "Clements")

Gist <- indoor_temps |> 
  filter(unit == "Gist")

Stiles <- indoor_temps |> 
  filter(unit == "Stiles")

Garza_West <- indoor_temps |> 
  filter(unit == "Garza West")

McConnell <- indoor_temps |> 
  filter(unit == "Mcconnell")

Clemens <- indoor_temps |> 
  filter(unit == "Clemens")

Roach <- indoor_temps |> 
  filter(unit == "Roach")

Wallace <- indoor_temps |> 
  filter(unit == "Wallace")

Stevenson <- indoor_temps |> 
  filter(unit == "Stevenson")

Dalhart <- indoor_temps |> 
  filter(unit == "Dalhart")

Hutchins <- indoor_temps |> 
  filter(unit == "Hutchins")
```

This code chunk will filter the activation data to seperate by unit.

```{r}
Middleton_activation <- activation_status |> 
  filter(unit == "Middleton")

Robertson_activation <- activation_status |> 
  filter(unit == "Robertson")

Gist_activation <- activation_status |> 
  filter(unit == "Gist")

Stiles_activation <- activation_status |> 
  filter(unit == "Stiles")

Wallace_activation <- activation_status |> 
  filter(unit == "Wallace")

Stevenson_activation <- activation_status |> 
  filter(unit == "Stevenson")

Hutchins_activation <- activation_status |> 
  filter(unit == "Hutchins")
```


## Joining the data

This set of code chunks will combine each unit with the corresponding station and find the difference in temperature between the two.

```{r}
#| label: Middleton

Middleton_comp <- left_join(Middleton, KABI_temps, by = "date") |>
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Middleton_active <- Middleton_comp |> 
  mutate(status = case_when(
    between(date, as.Date("2023-08-04"), as.Date("2023-08-14"))~"active",
    between(date, as.Date("2023-08-02"), as.Date("2023-08-03"))~"adjacent",
    between(date, as.Date("2023-08-15"), as.Date("2023-08-16"))~"adjacent",
    TRUE ~ "inactive"))

Middleton_active
```

```{r}
#| label: Robertson

Robertson_comp <- left_join(Robertson, KABI_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Robertson_active <- Robertson_comp |> 
  mutate(status = case_when(
    between(date, as.Date("2023-08-04"), as.Date("2023-08-14"))~"active",
    between(date, as.Date("2023-08-17"), as.Date("2023-08-22"))~"active",
    between(date, as.Date("2023-08-02"), as.Date("2023-08-03"))~"adjacent",
    between(date, as.Date("2023-08-15"), as.Date("2023-08-16"))~"adjacent",
    between(date, as.Date("2023-08-23"), as.Date("2023-08-24"))~"adjacent",
    TRUE ~ "inactive"))

Robertson_active
```

```{r}
#| label: Clements

Clements_comp <- left_join(Clements, KAMA_temps, by = "date") |> 
    mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Clements_active <- Clements_comp |> 
  mutate(status = "inactive")

Clements_active
```

```{r}
#| label: Gist

Gist_comp <- left_join(Gist, KBPT_temps, by = "date") |> 
    mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Gist_active <- Gist_comp |> 
  mutate(status = case_when(
    between(date, as.Date("2023-08-03"), as.Date("2023-08-16"))~"active",
    between(date, as.Date("2023-08-01"), as.Date("2023-08-02"))~"adjacent",
    between(date, as.Date("2023-08-17"), as.Date("2023-08-18"))~"adjacent"))

Gist_active[is.na(Gist_active)] <- "inactive"

Gist_active
```

```{r}
#| label: Stiles

Stiles_comp <- left_join(Stiles, KBPT_temps, by = "date") |> 
    mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Stiles_active <- Stiles_comp |> 
    mutate(status = case_when(
    between(date, as.Date("2023-08-03"), as.Date("2023-08-16"))~"active",
    between(date, as.Date("2023-08-01"), as.Date("2023-08-02"))~"adjacent",
    between(date, as.Date("2023-08-17"), as.Date("2023-08-18"))~"adjacent"))

Stiles_active[is.na(Stiles_active)] <- "inactive"

Stiles_active
```

```{r}
#| label: Garza West

Garza_West_comp <- left_join(Garza_West, KBEA_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Garza_West_active <- Garza_West_comp |> 
  mutate(status = "inactive")

Garza_West_active
```

```{r}
#| label: McConnell

McConnell_comp <- left_join(McConnell, KBEA_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

McConnell_active <- McConnell_comp |> 
  mutate(status = "inactive")

McConnell_active
```

```{r}
#| label: Clemens

Clemens_comp <- left_join(Clemens, KLBX_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Clemens_active <- Clemens_comp |> 
  mutate(status = "inactive")

Clemens_active
```


```{r}
#| label: Roach

Roach_comp <- left_join(Roach, KCDS_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Roach_active <- Roach_comp |> 
  mutate(status = "inactive")

Roach_active
```

```{r}
#| label: Wallace

Wallace_comp <- left_join(Wallace, KSNK_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Wallace_active <- Wallace_comp |> 
  mutate(status = case_when(
    between(date, as.Date("2023-08-09"), as.Date("2023-08-14"))~"active",
    between(date, as.Date("2023-08-07"), as.Date("2023-08-08"))~"adjacent",
    between(date, as.Date("2023-08-15"), as.Date("2023-08-16"))~"adjacent"))

Wallace_active[is.na(Wallace_active)] <- "inactive"

Wallace_active
```

```{r}
#| label: Stevenson

Stevenson_comp <- left_join(Stevenson, KVCT_temps, by = "date") |> 
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Stevenson_active <- Stevenson_comp |> 
  mutate(status = "inactive")

Stevenson_active
```

```{r}
#| label: Dalhart

Dalhart_comp <- left_join(Dalhart, KDHT_temps, by = "date") |>
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Dalhart_active <- Dalhart_comp |> 
  mutate(status = "inactive")

Dalhart_active
```

```{r}
#| label: Hutchins

Hutchins_comp <- left_join(Hutchins, KRBD_temps, by = "date") |>
  mutate(difference = abs(temperature - hourly_temp)) |> 
  select(date, unit, temperature, station, hourly_temp, rh, difference)

Hutchins_active <- Hutchins_comp |>
  mutate(status = case_when(
    between(date, as.Date("2023-08-09"), as.Date("2023-08-15"))~"active",
    between(date, as.Date("2023-08-17"), as.Date("2023-08-29"))~"active",
    between(date, as.Date("2023-08-07"), as.Date("2023-08-08"))~"adjacent",
    between(date, as.Date("2023-08-16"), as.Date("2023-08-16"))~"adjacent",
    between(date, as.Date("2023-08-30"), as.Date("2023-08-31"))~"adjacent",
    .default = "inactive"))

Hutchins_active
```

This code chunk joins the data frames together.

```{r}
#|label: joining all frames

all_comps <- bind_rows(Middleton_active, Robertson_active, Clements_active, Gist_active, Stiles_active, Garza_West_active, McConnell_active, Clemens_active, Roach_active, Wallace_active, Stevenson_active, Dalhart_active, Hutchins_active) |> 
  rename(unit_temp = temperature, station_code = station, station_temp = hourly_temp, temp_diff = difference)

all_comps
```

## Exporting comparison

This code chunk will export the data.

```{r}
#| label: exporting

all_comps |> 
  write_rds("data-processed/pearson-final-comparison.rds")
```

